Target Markdown

### 2023-04-27 _targets.Rmd
new topic model implemented

   tar_target(topic_model_input,
              make_topic_model_input(all_pubs)),

    tar_target(topic_number,
              find_topic_number(topic_model_input),
                format = "qs"),
    tar_target(topic_model,
               make_topic_model(topic_model_input, topic_number),
                format = "qs")

>>>>

   tar_target(topic_model_input,
              make_topic_model_input(random_pubs)),
   tar_target(topic_number,
              find_topic_number(topic_model_input),
                format = "qs"),
   tar_target(topic_model_original,
               make_topic_model(topic_model_input, topic_number),
                format = "qs"),
   tar_target(topic_model_input_addition,
              make_topic_model_input_addition(all_pubs)),
   tar_target(topic_model,
               make_topic_model_addition(topic_model_input_addition, topic_model_original),
                format = "qs")
